### 2014-01-16 inst/doc/README.Rmd
editing constructor for eml, avoid defining ID in eml prototype as the id is then not unique byt re-used through-out the session
Fixes #88 upstream (inst/doc/README.Rmd)

We can also publish to the KNB (Knowledge Network for Biocomplexity, a data repository provided by NCEAS) using the `dataon` R package.  KNB offers several advantages over alternative repositories such as figshare or [Dryad](http://datadryad.org) when publishing EML metadata. The KNB "speaks" EML, so it is unnecessary to provide repository-specific additional metadata such as description, category or tag -- all necessary information will be extracted from the EML. This is also much more thorough than other repositories: we can search the KNB network by specific taxonomic or geographic coverage, or even down at the level of individual attribute or column headings, rather than being limited to more generic metadata.  Lastly, KNB is a member node of the DataONE repository, making the resulting data files immediately part of a much larger network for ecological, earth and environmental science data.

@@

```{r publish_knb, eval=FALSE}
ids <- eml_publish("reml_example.xml", destination="KNB", permanent=FALSE)
```

@@

<-- Too detailed for this vignette

>>>>

We can also publish to the KNB (Knowledge Network for Biocomplexity,
a data repository provided by NCEAS) using the `dataone` R package.
KNB offers several advantages over alternative repositories such
as figshare or [Dryad](http://datadryad.org) when publishing EML
metadata. The KNB "speaks" EML, so it is unnecessary to provide
repository-specific additional metadata such as description, category or
tag -- all necessary information will be extracted from the EML. This is
also much more thorough than other repositories: we can search the KNB
network by specific taxonomic or geographic coverage, or even down at
the level of individual attribute or column headings, rather than being
limited to more generic metadata.  Lastly, KNB is a member node of the
DataONE repository, making the resulting data files immediately part of a
much larger network for ecological, earth and environmental science data.

@@

```{r publish_knb}
ids <- eml_publish("reml_example.xml", destination="KNB", permanent=FALSE)
```

@@

<--! Too detailed for this vignette
